{fairmetrics}: An R package for group fairness evaluation

### 2025-06-02 paper.Rmd
Fix typo.

-   **Brier Score Parity:** Compares the Brier score (i.e., the mean squared error of predicted probabilities) across groups, evaluating differences in calibration.

>>>>

-   **Brier Score Parity:** Compares the Brier score (i.e., the mean squared error of the predicted probabilities) across groups, evaluating differences in calibration.
